
\newcommand\ModelDescription[0]{ 
A node to insert is a place with a token.\\
The model of a node insertion in a CAN network is divided into an insertion in an empty CAN and an insertion in a non empty CAN. To do so, we use a counter place and a place with a token to check the CAN network status.\\
The insertion in an empty CAN follows a straight path and can be achieved without any constraint. Once the insertion done, the counter place takes one more token.\\
On the other hand, the insertion in a non empty CAN leads to an "AskSharing" place. At this point, the node has to ask an other node to share its space in the CAN. A node can send its request to one inserted node only.\\
If N is the number of nodes to insert, a node can choose one inserted node among all others. This is why we have N-1 possible paths to ask a request. And for the same reason, we also have N-1 paths for entering answer of the request.\\
We have to note that this model uses a multi-stride and sequential functioning on this part of the process.\\
The answer may be an acceptation -so the node will be inserted- or a denial -the node can retry its insertion by repeating the process. \\

H: First insertion is always in an empty CAN\\
H: Processes exchange via asynchronous communication\\

}

\newcommand\ModelReference[0]{
This model was described in:
Sylvia Ratnasamy,Paul Francis,Mark Handley,Richard Karp,Scott Shenker (2001). {\em A Scalable Content-Addressable Network}. \\
\url{https://dl.acm.org/doi/pdf/10.1145/383059.383072}
}


